%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Weiwu}{Pang}{ 
\href{mailto:weiwupan@usc.edu}{weiwupan@usc.edu} | 323.791.1024
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.30\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Southern California}
\location{Los Angeles, CA}
\location{Expected May 2018}
\location{Cum. GPA: 3.81 / 4.0 \\
Viterbi School of Engineering \\
Dean's List (All Semesters) }
\sectionsep

\descript{B.S. Computer Science}
\location{Major GPA: 3.78 / 4.0}
\sectionsep

\descript{B.S. Electrical Engineering}
\location{Emphasis in Computer Engineering}
\location{Major GPA: 3.81 / 4.0}

\sectionsep

%\subsection{Shenzhen Middle School}
%\location{Grad. May 2014|  Shenzhen, China}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\section{Links} 
%Github:// \href{https://github.com/deedydas}{\custombold{deedydas}} \\
%LinkedIn://  \href{https://www.linkedin.com/in/debarghyadas}{\custombold{debarghyadas}}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Technical SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\descript{Programming Languages:}
\location{Over 10000 lines:}
C++ \textbullet{} Java \textbullet{}  Matlab \\
\location{Over 5000 lines:}
C \textbullet{}  Assembly \textbullet{} \LaTeX\ \\ 
\descript{Technologies/Environment:}
CUDA \textbullet{} Android \textbullet{} iOS \textbullet{} \\
Windows \textbullet{} Linux
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\descript{Computer Science:}
Software Development \\
Software Engineering \\
Data Structure and Algorithm \\
Computer and Network Security \\
\descript{Electrical Engineering:}
Computer Network \\
Computer Systems Organization \\
Undergrad Thesis {\footnotesize \textit{\textbf{(Power Management System on GPUs)}}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Work Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{On-campus Work} 
\descript{Course Producer}
\location{Jan 2016 - Present}
Undergraduate Teach Assist. for C++ Data Structure and Algorithm Course

\descript{Math Tutor for Calculus}
\location{Jan 2016 - June 2016}
Hold tutor sessions for students who need helps in Calculus I, II and III
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.68\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Internship}
\runsubsection{GOOGLE INC.}
\descript{| Software Engineering Intern}
\location{May 2017 – August 2017 | Sunnyvale, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
	\item Interned in Global Software Load Balancer Team and worked on GSLB Reliability(GSLB 345) project.
	\item Hardened the coverage of the existing GSLB Fuzz Test framework from less than 10\% to 50\%.
	\item Designed and implemented a LogCollector Server that retrieve RPC logs from GSLB servers.
\end{tightemize}
\sectionsep

\section{Projects}

\runsubsection{ParkHere}
\descript{| Course Project: A P2P Resource Sharing Platform for Parking Space"}
\location{Sept 2016 – Dec 2016 | Los Angeles, CA}
\begin{tightemize}
	\item Designed the client-server architecture.
	\item Built the server in Java and maintained it on AWS and Digital Ocean server.
	\item Designed and implemented the backend of the Android client.
	\item Tested client side functionality using JUnit library.
	\item Implemented communication between server and clients with RPC protocals.
	\item Built MySQL database and authentication functionality.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Open Acceleration Systems (OASYS) Research Lab}
\descript{| Undergraduate Researcher}
\location{May 2016 – Present | Los Angeles, CA}
Worked with Professor \textbf{\href{http://oasys.isi.edu/profile.php?id=1}{Young H. Cho}} to create a power management software package that is able to improve power efficiency and manufacture yield rate for modern CPUs and GPUs.
\begin{tightemize}
	\item Designed an algorithm that utilizes Longest-Common-Ancestor(LCA) to generate graphs of possible runtime execution trace of any C/C++ program.
	\item Built the software prototype using multi-threading and shared memory to actively collect time-stamp and power information.
	\item Implemented MATLAB program to extracted CPU's subcomponents' power weight.
	\item Wrote test benches to research on NVIDIA's GPU runtime scheduling detail on CUDA parallel computing platform.
	\item Utilized Mccdaq datalogger and Universal Library(UL) to developed a GPU power monitor program.
\end{tightemize}
\sectionsep

\runsubsection{Vilesov Research Group}
\descript{| Undergraduate Researcher}
\location{Feb 2016 – Present | Los Angeles, CA}
Implemented an algorithm in MATLAB to process single-shot femtosecond X-ray coherent diffractive images. Received scholarship from USC Undergraduate Research Associates Program.
\begin{tightemize}
	\item Collaborated in an experiment hosted in SLAC National Accelerator Laboratory and utilized psana framework to analyze data in real time.
	\item Reconstructed and optimized old algorithm in MATLAB. The performance get 80\% better.
	\item Utilized auto-correlation technique to calculate droplet radius at different angles.
	\item Utilized lsqcurvefit and simulated annealing to process the diffraction pattern and fit the droplet model.
\end{tightemize}
\sectionsep





\end{minipage} 
\end{document}  \documentclass[]{article}
